An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-12 EconGrowth.Rnw
Minor edits on the paper.

\section*{To-do List}
\begin{itemize}
\item{Heun: Add base fit red dots to all cloud plots.}
      \begin{itemize}
      \item{SF}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{CES}
      \item{CESe}
      \item{LINEX}
      \end{itemize}
\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\item{\st{Heun: Add option for $m = 1$ in single-factor models.}}
\item{\st{Heun: Re-implement confidence interval calculations to use
resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Include scatter graphs for model parameters 
estimated by resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
\item{\st{Heun: Make smaller scatter plots for resample coefficients for those 
countries where $u$ is involved.}}
\item{\st{Heun: Add a table that shows the fraction of unconverged resample fits
for each model, energy type, and factor.}}
\item{\st{Heun: Get AIC calculations working again.}}
\end{itemize}

@@

\begin{itemize}
\item{capital stock ($k$) has increased more than the average 
      of energy ($e$) and labor ($l$), i.e. if $\rho_k >$ 1, or}
\item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
\end{itemize}

\noindent According to the LINEX model, an economy that can increase 
capital stock ($k$) without a commensurate increase in labor ($l$) 
and energy ($e$) will experience an increase in output ($y$) in excess 
of its increase of energy consumption ($e$), because $A$ will be 
greater than 1. Similarly, an economy benefits by increasing labor ($l$) 
without a commensurate increase in energy ($e$). Thus, $\rho_k$ is an 
efficiency of using labor and energy to make capital available to the 
economy, and $\rho_l$ is an efficiency of using energy to make labor 
available to the economy. $a_0$ represents the overall importance 
of these efficiencies, and $c_t$ represents the relative importance 
of the labor efficiency term compared to the capital stock efficiency term. 
We treat $a_0$ and $c_t$ as fitting parameters; 
both are assumed constant with respect to time.

>>>>

\section*{To-do List}
\begin{itemize}
\item{Pruim: Add base fit red dots to all cloud plots.}
      \begin{itemize}
      \item{SF}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{CES}
      \item{CESe}
      \item{LINEX}
      \end{itemize}
\item{Heun: Figure out why CESe for ZA with $x$ fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\item{\st{Heun: Add option for $m = 1$ in single-factor models.}}
\item{\st{Heun: Re-implement confidence interval calculations to use
resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Include scatter graphs for model parameters 
estimated by resampling methods.}}
      \begin{itemize}
      \item{\st{SF}}
      \item{\st{CD}}
      \item{\st{CDe}}
      \item{\st{CES}}
      \item{\st{CESe}}
      \item{\st{LINEX}}
      \end{itemize}
\item{\st{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}}
\item{\st{Heun: Make smaller scatter plots for resample coefficients for those 
countries where $u$ is involved.}}
\item{\st{Heun: Add a table that shows the fraction of unconverged resample fits
for each model, energy type, and factor.}}
\item{\st{Heun: Get AIC calculations working again.}}
\end{itemize}

@@

\begin{itemize}
\item{capital stock ($k$) has increased more than the average 
      of labor ($l$) and energy ($e$), i.e. if $\rho_k >$ 1, or}
\item{labor ($l$) has increased more than energy ($e$), i.e. if $\rho_l >$ 1.}
\end{itemize}

\noindent According to the LINEX model, an economy that can increase 
capital stock ($k$) without a commensurate increase in labor ($l$) 
and energy ($e$) will experience an increase in output ($y$) in excess 
of its increase of energy consumption ($e$), because $A$ will be 
greater than 1. Similarly, an economy benefits by increasing labor ($l$) 
without a commensurate increase in energy ($e$). Thus, $\rho_k$ is an 
efficiency of using additional labor and energy to make 
additional capital stock available to the economy, 
and $\rho_l$ is an efficiency of using additional energy to make 
additional labor available to the economy. 
$a_0$ represents the overall importance of these efficiencies, 
and $c_t$ represents the relative importance 
of the labor efficiency term compared to the capital stock efficiency term. 
We treat $a_0$ and $c_t$ as fitting parameters; 
both are assumed constant with respect to time.
